5 designs and 5 iterations and 3 granularities all of whose categories change

### 2021-09-29 main.Rmd
methodology subsection 1: finding significant granularities done

For each key variable, the raw smart meter data is indexed by time and comprises values of several variables of interest (measurement variables) at each time point. This sequence, though, could be depicted in a variety of ways. One sequence could reflect the distribution of hourly consumption over a single day, while another could indicate consumption over a week or a year. The sequence of measured variables throughout each category of any cyclic granularity could be regarded as a single data generating process. It is beneficial to evaluate those cyclic granularities that are significant for the majority of customers or noteworthy in an electricity-behavior context, so that when the customers are grouped, we can expect to observe some interesting patterns across the categories of the cyclic granularities considered.

- _Distance metric_

>>>>

For each key variable, the raw smart meter data is a sequence that is indexed by time and comprises values of several variables of interest (measurement variables) at each time point. This sequence, though, could be depicted in a variety of ways. A shuffling of the raw sequence could reflect the distribution of hourly consumption over a single day, while another could indicate consumption over a week or a year. These temporal deconstructions of a time period into units such as hour-of-day, work-day/weekend, called cyclic temporal granularities, are useful for exploring repetitive patterns in time series data that get lost in the linear representation of time. However, it is advantageous to consider those cyclic granularities across which there is a significant repetitive pattern for the majority of customers or noteworthy in an electricity-behavior context, because when the customers are grouped, we can expect to observe some interesting patterns across the categories of the cyclic granularities considered.

- _Distance metrics_

The existing work on clustering probability distributions assumes we have an iid sample $f_1(v),\dots,f_n(v)$, where $f_i(v)$ denotes the distribution from observation $i$ over some random variable $v = \{v_t: t = 0, 1, 2, \dots, T-1\}$ observed across $T$ time points. In our work, we are using $i$ as denoting a customer and the underlying variable as the electricity demand. So $f_i(v)$ is the distribution of household $i$ and $v$ is electricity demand.

If we consider the sequence of measured variables for each category of any cyclic granularity to be from a single data generating process, we want to cluster distributions of the form $f_{i,j,k}(v)$, where $j$ and $k$ denote two granularities. For example, j=hour of day and k=day of week. We still want the households in clusters, but each household consists of a collection of probability distributions f_{i,h,d}(x) where $h=1,...,24$ and $d=1,...,7$. In this example (hour of day/day of week), we would have $24*7=168$ distributions per household if we consider interaction of the households or $24+7=31$ distributions if individual effect of granularities need to be considered. So we need a distance between collections of these univariate probability distributions. There could be several ways of considering such distances. We consider the following two approoaches:

### 2021-09-29 supplementary/distance-computation/real-data/04handpick-from356-mds.Rmd
methodology subsection 1: finding significant granularities done

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, echo = FALSE, message=FALSE, warning=FALSE)
library(readr)
library(tidyverse)
library(gravitas)
library(tsibble)
library(parallel)
library(magrittr)
library(GGally)
library(knitr)
library(patchwork)
library(caret)
library(plotly)
```

@@

distance <- wkndwday %>% 
  left_join(moy, by = c("item1", "item2")) %>% 
  left_join(hod, by = c("item1", "item2")) %>% 
  rename("wkndwday" ="distance.x",
         "moy" = "distance.y",
         "hod" = "distance") %>%
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2))) 
# for hod MDS scale

total_distance <- distance %>% 
  mutate(total = hod)

@@

total_distance_wide$`8143599` <- NA

total_distance_wide <- bind_rows(total_distance_wide, c(item1=11590442))

mds_data <- total_distance_wide[-1]  %>% mutate_all(~replace(., is.na(.), 0))

mds <- mds_data %>% t() %>% as.dist() %>% cmdscale() %>% as_tibble()
colnames(mds) <- c("mds1.hod", "mds2.hod")

mds_hod <- bind_cols(mds, customer_id = mds_data %>% t() %>% rownames()) # since cmdscale is on transpose # because it only considers lower traingular matrix

@@

total_distance <- distance %>% 
  mutate(total = moy)

total_distance_wide$`8143599` <- NA

total_distance_wide <- bind_rows(total_distance_wide, c(item1=11590442))

mds_data <- total_distance_wide[-1]  %>% mutate_all(~replace(., is.na(.), 0))

mds <- mds_data %>% t()%>% as.dist()  %>% cmdscale() %>% as_tibble()
colnames(mds) <- c("mds1.moy", "mds2.moy")
mds_moy <- bind_cols(mds, customer_id = mds_data %>% t() %>% rownames())

@@

total_distance <- distance %>% 
  mutate(total = wkndwday)

total_distance_wide <- total_distance %>% pivot_wider(-c(2:5), 
                               names_from = item2,
                               values_from = total)
total_distance_wide$`8143599` <- NA

total_distance_wide <- bind_rows(total_distance_wide, c(item1=11590442))

mds_data <- total_distance_wide[-1]  %>% mutate_all(~replace(., is.na(.), 0))

mds <- mds_data %>% t() %>% as.dist() %>% cmdscale() %>% as_tibble()
colnames(mds) <- c("mds1.wkndwday", "mds2.wkndwday")
mds_wkndwday <- bind_cols(mds, customer_id = mds_data %>% t() %>% rownames())

# wkndwday+moy+

@@

# robust_scale <-  function(x){
#   (x - stats::median(x))/(stats::IQR(x))
# }
# 
# scaled_var <- apply(distance[-c(1, 2)], 2, robust_scale) %>% as_tibble()
# 
# 
# distance$wkndwday <- scaled_var$wkndwday
# distance$hod <- scaled_var$hod
# distance$moy <- scaled_var$moy
#

total_distance <- distance %>% 
  mutate(total = wkndwday + moy + hod)

total_distance_wide$`8143599` <- NA

total_distance_wide <- bind_rows(total_distance_wide, c(item1=11590442))

mds_data <- total_distance_wide[-1]  %>% mutate_all(~replace(., is.na(.), 0))

mds <- mds_data %>% t()%>% as.dist()  %>% cmdscale() %>% as_tibble()
colnames(mds) <- c("mds1.total", "mds2.total")
mds_total <- bind_cols(mds, customer_id = mds_data %>% t() %>% rownames())

@@

# robust_scale <-  function(x){
#   (x - stats::median(x))/(stats::IQR(x))
# }
# 
# elec_pick_wide_scaled <- apply(elec_pick_wide[-1], 2, robust_scale)

@@

mds_wpd <- bind_cols(mds, customer_id = elec_pick_wide$customer_id)%>% mutate(customer_id = as.character(customer_id))

mds_all <- mds_hod %>% 
  left_join(mds_moy, by = "customer_id") %>% 
  left_join(mds_wkndwday, by = "customer_id") %>% 
  left_join(mds_total, by = "customer_id") %>% 
  left_join(mds_wpd, by = "customer_id") %>% 
  select(customer_id, everything())

mds_all
```

@@

@@

subplot(mds_total, mds_hod, mds_moy ,mds_wkndwday, nrows = 2, titleX = TRUE) %>%
  layout(showlegend = FALSE) %>%
  highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = 0.2, off = "plotly_deselect") 
```

@@

```{r wpd-total}
# subplot(mds_wpd, mds_total, nrows = 1, titleX = TRUE) %>%
#   layout(showlegend = FALSE) %>%
#   highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = 0.2, off = "plotly_deselect") 
```

@@

sm_hod <- gravitas::create_gran(elec_356_raw, "hour_day")

sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(customer_id, hour_day, general_supply_kwh) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)

data_heatmap <- sm_quantiles_ref %>% 
 left_join(elec_pick %>% distinct(customer_id)) %>% 
  mutate(categories_serial_id = as.factor(categories_serial_id)) %>% 
  mutate(customer_id = as.character(customer_id))

data_heatmap_new <- data_heatmap %>%
left_join(mds_all, by = "customer_id")

@@

 # initiate a plotly object
 base <- plot_ly(tx, color = I("black")) %>%
   group_by(customer_id)
#
 quantile_plot <- base %>%
   group_by(customer_id) %>%
   add_lines(x = ~ categories_serial_id, y = ~`50%`, color = ("black")) %>%
   add_ribbons(x = ~categories_serial_id,
               ymin = ~`25%`,
               ymax = ~`75%`, color = I("lightblue"), alpha = (0.5))%>%
   layout(showlegend = FALSE)

@@

subplot(mds_total, mds_wpd, quantile_plot, nrows = 2, widths = c(.6, .4), titleX = TRUE) %>% layout(showlegend = FALSE) %>% highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = .2, off = "plotly_deselect")

@@

#10850478
data_pick_one <- total_distance %>% filter(item1 %in% 
                            c(8486921)) %>% group_by(item1) %>% arrange(total) %>% head(5) %>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

#11013154
data_pick_two <- total_distance %>% filter(item1 %in% 
                            c(8181071)) %>% group_by(item1) %>% arrange(total) %>% head(5)%>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

@@

@@

# data_pick_cust <- bind_rows(
# unique(c(data_pick_one$item1,data_pick_one$item2)) %>% as_tibble(),    unique(c(data_pick_two$item1,data_pick_two$item2)) %>% as_tibble(), c(11013154, 11045304, 11048034,11139841,11156027,11006388) %>% as_tibble(), .id = "design")
#

data_pick_cust <- bind_rows(
unique(c(data_pick_one$item1,data_pick_one$item2)) %>% as_tibble(), unique(c(data_pick_two$item1,data_pick_two$item2)) %>% as_tibble(), unique(c(data_pick_three$item1,data_pick_three$item2)) %>% as_tibble(), .id = "design")

@@

data_heatmap %>% 
  ggplot(aes(x = categories_serial_id)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id)) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") + theme_bw()

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, echo = FALSE, message=FALSE, warning=FALSE)
library(readr)
library(tidyverse)
library(gravitas)
library(tsibble)
library(parallel)
library(magrittr)
library(GGally)
library(knitr)
library(patchwork)
library(caret)
library(plotly)
library(gracsr)
library(here)
```

@@

distance <- wkndwday %>% 
  left_join(moy, by = c("item1", "item2")) %>% 
  left_join(hod, by = c("item1", "item2")) %>% 
  rename("wkndwday" ="distance.x",
         "moy" = "distance.y",
         "hod" = "distance") %>%
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

create_mds_gran <- function(total_distance){

@@

rownames(total_distance_wide) <- total_distance_wide$item1

#  changing to a lower traingular matrix as dist only takes lower traingular matrix (so in way tranposing it but tidyverse style, also creating a diagonal 0 with DM otherwise as.dist changing value)
mds_data <- total_distance_wide %>% 
  mutate_all(~replace(., is.na(.), 0)) %>%
   tibble::rownames_to_column() %>%  
   select(-item1) %>% 
   pivot_longer(-rowname) %>% 
   pivot_wider(names_from=rowname, values_from=value)

df <- mds_data[-1] %>% as.matrix()
DM <- matrix(0, ncol(mds_data), ncol(mds_data))
DM[lower.tri(DM)] = df[lower.tri(df, diag=TRUE)]

f = as.dist(DM)

first_lot <- mds_data %>% names()
id <- c(first_lot[-1], mds_data$name[nrow(mds_data)])

mds  = cmdscale(f)
rownames(mds) = id
colnames(mds) = c("mds1", "mds2")

mds_hod <- bind_cols(mds, customer_id = id)

mds_hod
 }

# for hod MDS scale

total_distance_hod <- distance %>% 
  mutate(total = hod)

mds_hod <- create_mds_gran(total_distance_hod)

colnames(mds_hod) <- c("mds1.hod", "mds2.hod", "customer_id")

@@

total_distance_moy <- distance %>% 
  mutate(total = moy)

mds_moy <- create_mds_gran(total_distance_moy)

colnames(mds_moy) <- c("mds1.moy", "mds2.moy", "customer_id")

@@

total_distance_wkndwday <- distance %>% 
  mutate(total = wkndwday)

mds_wkndwday <- create_mds_gran(total_distance_wkndwday)

colnames(mds_wkndwday) <- c("mds1.wkndwday", "mds2.wkndwday", "customer_id")

@@

total_distance_total <- distance %>% 
  mutate(total = wkndwday/2 + moy/12 + hod/24)

mds_total <- create_mds_gran(total_distance_total)

colnames(mds_total) <- c("mds1.total", "mds2.total", "customer_id")

```{r wpd-mds}

@@

@@

mds_wpd <- bind_cols(mds, customer_id = elec_pick_wide$customer_id)%>% mutate(customer_id = as.character(customer_id))
```

```{r mds-all}
mds_all <- mds_hod %>% 
  left_join(mds_moy, by = "customer_id") %>% 
  left_join(mds_wkndwday, by = "customer_id") %>% 
  left_join(mds_total, by = "customer_id") %>% 
  left_join(mds_wpd, by = "customer_id") %>% 
  select(customer_id, everything())

@@

```{r mds-all}

@@

subplot(mds_total, mds_hod, mds_moy ,mds_wkndwday, titleX = TRUE) %>%
  layout(showlegend = FALSE) %>%
  highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = 0.2, off = "plotly_deselect") 
```

@@

```{r wpd-total}
subplot(mds_wpd, mds_total, nrows = 1, titleX = TRUE) %>%
  layout(showlegend = FALSE) %>%
  highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = 0.2, off = "plotly_deselect")
```

@@

quantile_hod <- quantile_gran(elec_356_raw, gran1 = "hour_day", quantile_prob_val = quantile_prob_graph)

quantile_moy <- quantile_gran(elec_356_raw, gran1 = "month_year", quantile_prob_val = quantile_prob_graph)

quantile_wkndwday <- quantile_gran(elec_356_raw, gran1 = "wknd_wday", quantile_prob_val = quantile_prob_graph)

quantile_data <- bind_rows(quantile_hod, quantile_moy, quantile_wkndwday)

elec_pick_wide <- elec_pick %>% pivot_wider(c(3:5), names_from = "x_variable", values_from = wpd)

data_heatmap <- quantile_data %>% 
 left_join(elec_pick_wide) %>% 
  mutate(customer_id = as.character(customer_id))

# %>% 
#   mutate(categories_serial_id = as.factor(categories_serial_id)) %>% 
#   mutate(customer_id = as.character(customer_id))

data_heatmap_new <- data_heatmap %>%
left_join(mds_all, by = "customer_id") %>%  pivot_wider( names_from = quantiles, values_from = quantiles_values)

@@

 # initiate a plotly object
 base <- plot_ly(tx, color = I("black")) %>%
   group_by(customer_id)
#
 quantile_plot <- base %>% 
   group_by(customer_id, gran) %>%
   add_lines(x = ~ category, y = ~`50%`, color = ("black")) %>%
   add_ribbons(x = ~category,
               ymin = ~`25%`,
               ymax = ~`75%`, color = I("lightblue"), alpha = (0.5))%>%
   layout(showlegend = FALSE)

@@

subplot(mds_total, quantile_plot, nrows = 2, widths = c(.6, .4), titleX = TRUE) %>% layout(showlegend = FALSE) %>% highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = .2, off = "plotly_deselect")

# hod

data_heatmap_hod <- data_heatmap_new %>% filter(gran == "hour_day") %>% 
  mutate(category = as.integer(category))
tx <- highlight_key(data_heatmap_hod, ~customer_id)

 # initiate a plotly object
base <- plot_ly(tx, color = I("black")) %>%
   group_by(customer_id)

 quantile_plot <- base %>%
   group_by(customer_id, gran) %>%
   add_lines(x = ~ category, y = ~`50%`, color = ("black")) %>%
   #add_ribbons(x = ~category,
    #           ymin = ~`25%`,
    #           ymax = ~`75%`, color = I("lightblue"), alpha = (0.5))%>%
   layout(showlegend = FALSE)

subplot(mds_hod, quantile_plot, widths = c(.6, .4), titleX = TRUE) %>% layout(showlegend = FALSE) %>% highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = .2, off = "plotly_deselect", persistent = TRUE)
#

```
```{r}
# hod

data_heatmap_hod <- data_heatmap_new %>% filter(gran == "hour_day") %>% mutate(category = as.integer(category))

tx <- highlight_key(data_heatmap_hod, ~customer_id)

 # initiate a plotly object
base <- plot_ly(tx, color = I("black")) %>%
   group_by(customer_id)

 quantile_plot <- base %>%
   group_by(customer_id, gran) %>%
   add_lines(x = ~ category, y = ~`50%`, color = ("black")) %>%
   #add_ribbons(x = ~category,
    #           ymin = ~`25%`,
    #           ymax = ~`75%`, color = I("lightblue"), alpha = (0.5))%>%
   layout(showlegend = FALSE)

 mds_hod <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.moy, y = ~ mds2.moy, text = ~customer_id)

subplot(mds_hod, quantile_plot, widths = c(.6, .4), titleX = TRUE) %>% layout(showlegend = FALSE) %>% highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = .2, off = "plotly_deselect")
```

@@

#10850478 8486921
data_pick_one <- total_distance %>% filter(item1 %in% 
                            c(8454221)) %>% group_by(item1) %>% arrange(total) %>% head(5) %>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

#11013154  8181071 11048034
data_pick_two <- total_distance %>% filter(item1 %in% 
                            c(8181071)) %>% group_by(item1) %>% arrange(total) %>% head(5)%>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

@@

data_pick_four <- total_distance %>% filter(item1 %in%
                            c(8653709)) %>% group_by(item1) %>% arrange(total) %>% head(5)%>%
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

@@

data_pick_cust <- bind_rows(
unique(c(data_pick_one$item1,data_pick_one$item2)) %>% as_tibble(),    unique(c(data_pick_two$item1,data_pick_two$item2)) %>% as_tibble(), c(11013154, 8495194, 8627007,10109182,10677705,8952846) %>% as_tibble(),unique(c(data_pick_four$item1,data_pick_four$item2)) %>% as_tibble(),
.id = "design")

# data_pick_cust <- bind_rows(
# unique(c(data_pick_one$item1,data_pick_one$item2)) %>% as_tibble(),    c(11013154, 8495194, 8627007,10109182,10677705,8952846) %>% as_tibble(), c(867773, 8240424, 8267102,8281608,8403312,8454235) %>% as_tibble(), .id = "design")

# c(11013154, 11045304, 11048034,11139841,11156027,11006388)

# data_pick_cust <- bind_rows(
# unique(c(data_pick_one$item1,data_pick_one$item2)) %>% as_tibble(), unique(c(data_pick_two$item1,data_pick_two$item2)) %>% as_tibble(), unique(c(data_pick_three$item1,data_pick_three$item2)) %>% as_tibble(), .id = "design")

@@

data_heatmap %>% 
  ggplot(aes(x = categories_serial_id)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id)) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))

@@

<!-- # mds_hod <- base %>% -->
<!--   # group_by(customer_id) %>% -->
<!--   # add_trace(x = ~mds1.hod, y = ~ mds2.hod, text = ~customer_id) -->

<!-- # hod_wide <- hod %>% -->
<!-- #   pivot_wider(names_from = item2, values_from = distance)%>% -->
<!-- #   mutate(item1 = as.integer(as.character(item1))) -->
<!-- #  -->
<!-- # hod_wide$`8143599` <- NA -->
<!-- #  -->
<!-- # hod_wide <- bind_rows(hod_wide, c(item1=11590442)) -->
<!-- #  -->
<!-- # mds_data <- hod_wide[-1]  %>% mutate_all(~replace(., is.na(.), 0)) %>% as.dist() %>% clust_gran() -->
<!-- #   -->

### 2021-09-29 supplementary/distance-computation/simulation-data/D3_I10_C1.Rmd
methodology subsection 1: finding significant granularities done

```{r change-var, echo=TRUE}
t = 300
n <- seq(0, n, 1)
g1 <- n %%2
g2 <- n %%3
g3 <- n %%5
mu1= c(0, 2)
mu2 = c(7, 5, 1)
mu3 = c(1, 2, 5, 3, 1)
```

@@

# _Granularities design_
```{r}
design = c("design-1", "design-2", "design-3", "design4", "design5")
g1 = c("no", "yes", "no", "no", "yes")
g2 = c("no", "no", "yes", "no", "yes")
g3 = c("no", "no", "no", "yes", "yes")
table <- tibble(design, g1, g2, g3) %>% kable()
table

@@

```{r}
generate_design <- function(t, mu1, mu2, mu3){

@@

g1_dvary <- rep(mu1, length.out= length(t))
g2_dvary <- rep(mu2, length.out= length(t))
g3_dvary <- rep(mu3, length.out= length(t))

design1 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dnull)
design2 = distributional::dist_normal(g1_dvary + g2_dnull + g3_dnull)
design3 = distributional::dist_normal(g1_dnull + g2_dvary + g3_dnull)
design4 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dvary)
design5 = distributional::dist_normal(g1_dvary + g2_dvary + g3_dvary)

data_bind <- tibble::tibble(
index = t,
g1 = g1,
g2 = g2,
g3 = g3,
design1 = distributional::generate(design1, times = 1) %>% unlist(),
design2 = distributional::generate(design2, times = 1) %>% unlist(),
design3 = distributional::generate(design3, times = 1) %>% unlist(),
design4 = distributional::generate(design4, times = 1) %>% unlist(),
design5 = distributional::generate(design5, times = 1) %>% unlist()
) %>% 
  pivot_longer(-c(1, 2, 3, 4), names_to = "design", values_to = "sim_data")

@@

t = 300
mu1= c(0, 2)
mu2 = c(7, 5, 1)
mu3 = c(1, 2, 5, 3, 1)

data_bind <- generate_design(t, mu1, mu2, mu3)

@@

```{r}
seed_len = seq(12345, 12349, 1)
bind_data_iter <- map(seq_len(length(seed_len)), function(x){
set.seed(seed_len[x])
data_bind <- generate_design(t, mu1, mu2, mu3)
}) %>% bind_rows(.id = "seed_id") %>% 
  mutate(customer_id = paste(design,seed_id, sep ="-"))

@@

groups = dist_mat%>% clust_gran(kopt = 5)
pred_group = paste("design",groups$group,sep = "") %>% as.factor()
actual_group = as.factor(bind_data_iter_tsibble %>%as_tibble %>% select(customer_id, design) %>% distinct() %>% pull(design))

@@

groups = dist_mat %>% 
  clust_gran(kopt = 5)

>>>>

```{r change-var, echo=TRUE}
t = 300
n <- seq(0, t, 1)
g1 <- n %%2
g2 <- n %%3
g3 <- n %%5
mu21= c(2, 0, 0)
mu22 = c(0, 2, 0)
mu23 = c(0, 0, 2)
mu3 = c(0, 0, 0, 0, 0)
```

@@

# _Granularities design_

@@

```{r}
generate_design <- function(t, mu21, mu22, mu23){

@@

g1_dvary <- rep(0, length.out= length(t))
g21_dvary <- rep(mu21, length.out= length(t))
g22_dvary <- rep(mu22, length.out= length(t))
g23_dvary <- rep(mu23, length.out= length(t))
g3_dvary <- rep(0, length.out= length(t))

design1 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dnull)
design2 = distributional::dist_normal(g1_dnull + g21_dvary + g3_dnull)
design3 = distributional::dist_normal(g1_dnull + g22_dvary + g3_dnull)
design4 = distributional::dist_normal(g1_dnull + g23_dvary + g3_dnull)

data_bind <- tibble::tibble(
index = t,
g1 = g1,
g2 = g2,
g3 = g3,
design1 = distributional::generate(design1, times = 1) %>% unlist(),
design2 = distributional::generate(design2, times = 1) %>% unlist(),
design3 = distributional::generate(design3, times = 1) %>% unlist(),
design4 = distributional::generate(design4, times = 1) %>% unlist(),
#design5 = distributional::generate(design5, times = 1) %>% unlist()
) %>% 
  pivot_longer(-c(1, 2, 3, 4), names_to = "design", values_to = "sim_data")

@@

data_bind <- generate_design(t, mu21, mu22, mu23)

@@

```{r}
seed_len = seq(12345, 12349, 1)
bind_data_iter <- map(seq_len(length(seed_len)), function(x){
set.seed(seed_len[x])
data_bind <- generate_design(t, mu21, mu22, mu23)
}) %>% bind_rows(.id = "seed_id") %>% 
  mutate(customer_id = paste(design,seed_id, sep ="-"))

@@

groups = dist_mat %>% clust_gran(kopt = 4)
pred_group = paste("design",groups$group,sep = "") %>% as.factor()
actual_group = as.factor(bind_data_iter_tsibble %>%as_tibble %>% select(customer_id, design) %>% distinct() %>% pull(design))

@@

groups = dist_mat %>% 
  clust_gran(kopt = 4)

### 2021-09-29 supplementary/distance-computation/simulation-data/D4_I10_C2.Rmd
methodology subsection 1: finding significant granularities done

```{r change-var, echo=TRUE}
t = 300
n <- seq(0, t, 1)
g1 <- n %%2
g2 <- n %%3
g3 <- n %%5
mu21= c(2, 0, 0)
mu22 = c(0, 2, 0)
mu23 = c(0, 0, 2)
mu3 = c(0, 0, 0, 0, 0)
```

@@

g1_dvary <- rep(0, length.out= length(t))
g21_dvary <- rep(mu21, length.out= length(t))
g22_dvary <- rep(mu22, length.out= length(t))
g23_dvary <- rep(mu23, length.out= length(t))
g3_dvary <- rep(0, length.out= length(t))

design1 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dnull)
design2 = distributional::dist_normal(g1_dnull + g21_dvary + g3_dnull)
design3 = distributional::dist_normal(g1_dnull + g22_dvary + g3_dnull)
design4 = distributional::dist_normal(g1_dnull + g23_dvary + g3_dnull)

@@

```{r}
seed_len = seq(12345, 12349, 1)
bind_data_iter <- map(seq_len(length(seed_len)), function(x){
set.seed(seed_len[x])
data_bind <- generate_design(t, mu21, mu22, mu23)
}) %>% bind_rows(.id = "seed_id") %>% 
  mutate(customer_id = paste(design,seed_id, sep ="-"))

>>>>

```{r change-var, echo=TRUE}
t = 300
n <- seq(0, t, 1)
g1 <- n %%2
g2 <- n %%3
g3 <- n %%5
mu11 = c(0, 5)
mu12 = c(0, 3)
mu21= c(2, 0, 0)
mu22 = c(0, 2, 0)
mu23 = c(0, 0, 2)
mu3 = c(0, 0, 0, 0, 0)
```

@@

g11_dvary <- rep(mu11, length.out= length(t))
g12_dvary <- rep(mu12, length.out= length(t))
g21_dvary <- rep(mu21, length.out= length(t))
g22_dvary <- rep(mu22, length.out= length(t))
g23_dvary <- rep(mu23, length.out= length(t))
g3_dvary <- rep(0, length.out= length(t))

design1 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dnull)
design2 = distributional::dist_normal(g11_dvary + g21_dvary + g3_dnull)
design3 = distributional::dist_normal(g12_dvary + g22_dvary + g3_dnull)
design4 = distributional::dist_normal(g1_dnull + g23_dvary + g3_dnull)

@@

```{r}
seed_len = seq(12345, 12399, 1)
bind_data_iter <- map(seq_len(length(seed_len)), function(x){
set.seed(seed_len[x])
data_bind <- generate_design(t, mu21, mu22, mu23)
}) %>% bind_rows(.id = "seed_id") %>% 
  mutate(customer_id = paste(design,seed_id, sep ="-"))
